Spatiotemporal models of species biomass split by maturity class

### 2019-08-27 analysis/VOCC/1-biomass-models.Rmd
add all surveys to biomass-model options

Region 
```{r}
 region <- "Both odd year surveys"
region <- "West Coast Vancouver Island"
#  region <- "West Coast Haida Gwaii"
```

@@

#update_spatial_model <- TRUE
```

>>>>

Region 
```{r}
 region <- "All synoptic surveys"
# region <- "Both odd year surveys"
# region <- "West Coast Vancouver Island"
# region <- "West Coast Haida Gwaii"
```

@@

if (region == "All synoptic surveys") {
  survey <- c("SYN QCS", "SYN HS", "SYN WCVI", "SYN WCHG")
  model_ssid <- c(1, 3, 4, 16)
  ssid_string <- paste0(model_ssid, collapse = "n")
  years <- NULL
}
```
